\chapter{Introduction}

\section{Course Information}

\begin{listu}
    \item \textbf{Instructor}: Malors Emilio Espinosa Lara
    \item \textbf{Office}: BA 6256
    \item \textbf{Email}: \href{mailto:srolam.espinosalara@mail.utoronto.ca}{srolam.espinosalara@mail.utoronto.ca}
    \item \textbf{TA}: Shuofeng Xu, Mohammad Honari and Mohammadmahdi Rafiei
    \item \textbf{Office Hours}
    \begin{table}[ht!]
        \centering
        \begin{tabular}{|c|c|c|}
            \hline
            LEC101, LEC2001 & Tuesday 9 - 11 (PB B250) & Thursday 10 - 11 (MP 202) \\
            \hline
            Instructor Office Hours & Monday 12 - 1 & BA6256 (My office) \\
            \hline
        \end{tabular}
    \end{table}
    \item There are \textbf{no tutorials} for this course.
\end{listu}

\subsection{Communication}

All communication will occur by U of T email. Feel free to contact the instructor via email to ask extra questions and doubts, corrections about homeworks, inquiries, etc. However, the following titles must be used in the subject of the email:

\begin{listu}
    \item \textbf{MAT301: Mark Correction}. Put this title whenever you feel a correction is needed in one of your homeworks or midterm.
    \item \textbf{MAT301: Math Doubt}. If you have a mathematical doubt.
    \item \textbf{MATH301: Administrative Issue}. If you have any other concern that doesn’t fall into the previous categories.
\end{listu}

\subsection{Evaluation Criteria}

We will follow the following grading scheme for this course.

\begin{table}[ht!]
    \centering
    \begin{tabular}{|c|c|}
        \hline
        10 Homeworks (drop the lowest scored one of the first five and of the last five) & 25\% \\
        \hline
        Midterm & 25\% \\
        \hline 
        Final Examination & 50\% \\
        \hline
    \end{tabular}
\end{table}

Notice that \bred{late homework submission are usually given mark zero}. Exceptions due to required accommodations or unexpected circumstances will be of course taken into account and discussed in a case by case basis. Please write to the instructor in these situations. 

Any grade curve that might occur will only be done over the final course mark and not for particular homework, midterm or final test.

\section{Important Dates}

The following are some of the dates relevant, and with respect, to MAT301:

\begin{table}[ht!]
    \begin{tabular}{|c|c|}
        \hline
        First day of classes of University & Monday, January 8 \\
        \hline
        First Lecture & Tuesday, January 9 \\
        \hline
        Family Day & February 19 (University Closed) \\
        \hline
        Winter Reading Week(No lectures, nor Office hours) & February 19 to 23 \\
        \hline
        Our Course Midterm & February 26, 19:00 - 21:00 (Venues TBA) \\
        \hline
        Good Friday & March 29 (University Closed) \\
        \hline
        Last day of classes & April 5 \\
        \hline
        Study Day & April 9 \\
        \hline
        Final Exam Period & April 10 - 30 \\
        \hline
    \end{tabular}
\end{table}

\section{Course Description}

This course covers Groups oriented to computations. In order to understand groups well, a solid background in \itblue{linear algebra} is required: matrices, determinants, eigenvalues, eigenvectors, etc. \itblue{Modular arithmetic} is also required, as well as some basic notions of \itblue{number theory}. 